### 2017-02-22 introduction.tex
title page format

>>>>

This paper is an extension of our work that appeared in RV 2016~\cite{Shi2016}.
We added the proof for Lemma~\ref{lem:mutation}, \ref{lem:sub} and
Theorem~\ref{the:equivalent}. We included new results that show the searching
cost (Fig.~\ref{fig:cost}), and details of the ARF protocol violations
(Section~\ref{subsec:arf}). Further, we reported the application of our
framework to a commercial product under development in
Section~\ref{subsec:xbox}.
